Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-12-16 MHCpaper/MHCsupp.tex
pooled fig fixed

\begin{figure}
 \begin{center}
   \begin{myenuma}
  \begin{tabular}{l@{\hspace{0.05\linewidth}}l}
    \item\aligntop{\includegraphics[height=1.7cm]{serial.svg}}\label{fig:serial_model}&
    \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\\[1.7cm]
    \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}&
    \item\aligntop{\includegraphics[height=2.5cm]{cascade.svg}}\label{fig:cascade_model}\\[2.5cm]
    \item\aligntop{\includegraphics[height=2.3cm]{pooled.svg}}\label{fig:pooled_model}&
    \item\aligntop{\includegraphics[height=2.3cm]{multistate_nonuni.svg}}\label{fig:nonuni_model}
  \end{tabular}
   \end{myenuma}
 \end{center}
  \caption[Transition probabilities for different models]{{Transition probabilities for different models.}
  Potentiation induces transitions indicated by orange arrows, depression indicated by blue arrows.
  States of strong/weak synaptic weight indicated by orange/blue circles.
  (\ref{fig:serial_model}) In the serial model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  The synaptic weight takes only two values, $\pm1$.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised  by these two values.
  The synaptic weight varies linearly in the interval $[-1,1]$.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  (\ref{fig:pooled_model}) In the pooled resource model,
  Several two-state synapses share resources that are required for potentiation and depression.
  These resources are depleted as more synapses are potentiated or depressed.
  This pool of synapses can be modelled as one compound synapse.
  (\ref{fig:nonuni_model}) In the non-uniform multistate model
  the synaptic weight varies linearly in the interval $[-1,1]$, similar to the multistate model, but the transition probabilities between adjacent states decays exponentially away from the central transition for both potentiation and depression.
  } \label{fig:models}
\end{figure}

@@

This model is parameterised by the range of values, $q\in[q\lmin,q\lmax]$, for potentiation and depression.
We will use the same values for potentiation in the wild-type asnd \KO\ models.
We will use larger values for depression in the \KO\ models than in the wild-type.
we consider a version of this model that has resource depletion for depression only, so that potentiation transition probabilities are unaffected by the number of potentiated synapses.
This is done by setting $q\pot\lmax=q\pot\lmin$.
The values of these parameters are listed in \autoref{fig:sim_results}\ref{tab:params}.

@@

For the other models, a numerical analysis is required, as shown in \autoref{fig:bal}.
\hypertarget{par:bal_scan}{To} see if learning is impaired with enhanced plasticity each relevant parameter was scanned over 10 values from 0.05 to 0.95, rejecting values that do not respect the inequalities:
$0 \leq f\dep\norm < f\dep\inc \leq 1$, for the pooled resource model $0 \leq q\dep_\text{min,WT} < q\dep_\text{min,\KO}, q\dep_\text{max,WT} < q\dep_\text{max,\KO}$ and $0 \leq q\pot\wt$, for the cascade model $0 \leq x\dep\wt < x\dep\ko \leq \frac{1}{2}$ and $0 \leq x\pot\wt \leq \frac{1}{2}$, and for the nonuniform multistate model $0 \leq x\dep\wt < x\dep\ko \leq 1$ and $0 \leq x\pot\wt \leq 1$.
In each case, the \KO\ potentiation parameter, $q\pot\ko$ for the pooled resource model and $x\pot\ko$ for the others, was adjusted to match the baseline mean synaptic weight. $\pr(0)\w$, with wild-type.

>>>>

\begin{figure}
 \begin{center}
   \begin{myenuma}
  \begin{tabular}{l@{\hspace{0.05\linewidth}}l}
    \item\aligntop{\includegraphics[height=1.7cm]{serial.svg}}\label{fig:serial_model}&
    \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\\[1.7cm]
    \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}&
    \item\aligntop{\includegraphics[height=2.5cm]{cascade.svg}}\label{fig:cascade_model}\\[2.5cm]
    \item\aligntop{\includegraphics[height=2.3cm]{pooled_deponly.svg}}\label{fig:pooled_model}&
    \item\aligntop{\includegraphics[height=2.3cm]{multistate_nonuni.svg}}\label{fig:nonuni_model}
  \end{tabular}
   \end{myenuma}
 \end{center}
  \caption[Transition probabilities for different models]{{Transition probabilities for different models.}
  Potentiation induces transitions indicated by orange arrows, depression indicated by blue arrows.
  States of strong/weak synaptic weight indicated by orange/blue circles.
  (\ref{fig:serial_model}) In the serial model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  The synaptic weight takes only two values, $\pm1$.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised  by these two values.
  The synaptic weight varies linearly in the interval $[-1,1]$.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  (\ref{fig:pooled_model}) In the pooled resource model,
  Several two-state synapses share resources that are required for potentiation and depression.
  These resources are depleted as more synapses are potentiated or depressed.
  This pool of synapses can be modelled as one compound synapse.
  (\ref{fig:nonuni_model}) In the non-uniform multistate model
  the synaptic weight varies linearly in the interval $[-1,1]$, similar to the multistate model, but the transition probabilities between adjacent states decays exponentially away from the central transition for both potentiation and depression.
  } \label{fig:models}
\end{figure}

@@

This model is parameterised by the range of values, $q\in[q\lmin,q\lmax]$, for potentiation and depression.
We will use the same values for potentiation in the wild-type asnd \KO\ models.
We will use larger values for depression in the \KO\ models than in the wild-type.
We consider a version of this model that has resource depletion for depression only, so that potentiation transition probabilities are unaffected by the number of potentiated synapses.
This is done by setting $q\pot\lmax=q\pot\lmin$.
The values of these parameters are listed in \autoref{fig:sim_results}\ref{tab:params}.

@@

For the other models, a numerical analysis is required, as shown in \autoref{fig:bal}.
\hypertarget{par:bal_scan}{To} see if learning is impaired with enhanced plasticity each relevant parameter was scanned over 10 values from 0.05 to 0.95 (or from 0.05 to 0.5 for the $x$ parameter of the cascade model), rejecting values that do not respect the inequalities:
$0 \leq f\dep\norm < f\dep\inc \leq 1$, for the pooled resource model $0 \leq q\dep_\text{min,WT} < q\dep_\text{min,\KO}, q\dep_\text{max,WT} < q\dep_\text{max,\KO} \leq 1$ and $0 \leq q\pot\wt \leq 1$, for the cascade model $0 \leq x\dep\wt < x\dep\ko \leq \frac{1}{2}$ and $0 \leq x\pot\wt \leq \frac{1}{2}$, and for the nonuniform multistate model $0 \leq x\dep\wt < x\dep\ko \leq 1$ and $0 \leq x\pot\wt \leq 1$.
In each case, the \KO\ potentiation parameter, $q\pot\ko$ for the pooled resource model and $x\pot\ko$ for the others, was adjusted to match the baseline mean synaptic weight. $\pr(0)\w$, with wild-type.
